Introducing SCM to a small company

### 2012-01-11 article.tex
loasdasd

\section{The Problem Company XXXXXXX}

@@

The company are programming Java and are using Eclipse as their tool.
With eclipse they have several different addons which makes it hard for them to use another tool. An approach building upon this platform, in the from of another plugin would therefore propably be the best solution.

WRITE MOAR HER3

@@

The configuration plan can be written in two different approaches.
cite{SCMPLAN} It can either be done before the implementation of SCM in a big bang approach or we can use a more iterative method and complete the plan meanwhile the project goes on.
Since we are new to the role as a configuration manager and don’t have a precise definition on the company and its details it might be too hard to go with the iterative approach.
This way we can start with the most important parts of the SCM plan in the beginning.

@@

A SCM plan is a good checklist for the configuration manager to check whether all is kept in mind for the SCM implementation or something is missed.
When all the checkpoints are completed we have a completed SCM plan to work upon and we know we have thought of all the details.
Once the configuration plan is completed it’s not finished.
Changes are often made to the project which will have impact on the plan, we therefore need to change the configuration plan as well so it is always updated.
This is one of the reasons why we need to have the configuration plan as a configuration item (CI) which we will describe later on in the paper.

>>>>

\section{The Problem Company}

@@

The company are programming Java and are using Eclipse as their tool.
With eclipse they have several different add-ons which makes it hard for them to use another tool. An approach building upon this platform, in the from of another plug-in would therefore probably be the best solution.

WRITE MORE HERE

@@

The configuration plan can be written in two different approaches.
cite{SCMPLAN} It can either be done before the implementation of SCM in a big bang approach or we can use a more iterative method and complete the plan meanwhile the project goes on.
Since we are new to the role as a configuration manager and don't have a precise definition on the company and its details it might be too hard to go with the iterative approach.
This way we can start with the most important parts of the SCM plan in the beginning.

@@

A SCM plan is a good checklist for the configuration manager to check whether all is kept in mind for the SCM implementation or something is missed.
When all the checkpoints are completed we have a completed SCM plan to work upon and we know we have thought of all the details.
Once the configuration plan is completed it's not finished.
Changes are often made to the project which will have impact on the plan, we therefore need to change the configuration plan as well so it is always updated.
This is one of the reasons why we need to have the configuration plan as a configuration item (CI) which we will describe later on in the paper.
